Efficient ancestry and mutation simulation with msprime 1.0

### 2021-08-09 paper.tex
added affiliation and funding support

% Bjarki
\affil[8]{FIXME: BJARKI's AFFILIATION}
% Castedo
\affil[9]{FIXME: CASTEDO's AFFILIATION}
% Jared, Murillo, Peter, Andy
\affil[10]{Department of Biology and Institute of Ecology and Evolution,
    University of Oregon}
% Ariella
\affil[11]{Department of Genetics, University of North Carolina at Chapel Hill}
% Gregor
\affil[12]{The Roslin Institute and Royal (Dick) School of Veterinary Studies,
    University of Edinburgh}
% Bing
\affil[13]{FIXME: BING's AFFILIATION}
% Winni
\affil[14]{FIXME: WINNI's AFFILIATION}
% Simon, Dom, Ivan
\affil[15]{Department of Human Genetics, McGill University}
% Michael
\affil[16]{FIXME: MICHAEL's AFFILIATION}
% Nathaniel
\affil[17]{FIXME: NATHANIEL's AFFILIATION}
% Consuelo
\affil[18]{National Laboratory of Genomics for Biodiversity (LANGEBIO),
    Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico}
% Saunack
\affil[19]{FIXME: SAUNACK's AFFILIATION}
% Thibaut
\affil[20]{Professorship for Population Genetics, Department of Life Science Systems, Technical University of Munich}
% Kevin
\affil[21]{Ecology and Evolutionary Biology, University of California at Irvine}
% Hugo
\affil[22]{FIXME HUGO's AFFILIATION}
% Jere
\affil[23]{FIXME: JERE'S AFFILIATION}
% Peter (second affil)
\affil[24]{Department of Mathematics, University of Oregon}

@@

\section*{Acknowledgements}
JK is supported by the Robertson Foundation.
Jere Koskela is supported in part by EPSRC grant EP/R044732/1.
ADK was supported by NIH awards R01GM117241 and R01HG010774.
Franz Baumdicker is funded by the Deutsche Forschungsgemeinschaft
EXC 2064/1 -- Project number 390727645, and EXC 2124 -- Project number 390838134.
Graham Gower was supported by a Villum Fonden Young Investigator award to Fernando Racimo (project no. 00025300).

>>>>

% Bjarki
\affil[8]{Leibniz Institute for Evolution and Biodiversity
Science, Museum f\"ur Naturkunde Berlin }
% Castedo
\affil[9]{FIXME: CASTEDO's AFFILIATION}
% Jared, Murillo, Peter, Andy
\affil[10]{Department of Biology and Institute of Ecology and Evolution,
    University of Oregon}
% Ariella
\affil[11]{Department of Genetics, University of North Carolina at Chapel Hill}
% Gregor
\affil[12]{The Roslin Institute and Royal (Dick) School of Veterinary Studies,
    University of Edinburgh}
% Bing
\affil[13]{FIXME: BING's AFFILIATION}
% Winni
\affil[14]{FIXME: WINNI's AFFILIATION}
% Simon, Dom, Ivan
\affil[15]{Department of Human Genetics, McGill University}
% Michael
\affil[16]{FIXME: MICHAEL's AFFILIATION}
% Nathaniel
\affil[17]{FIXME: NATHANIEL's AFFILIATION}
% Consuelo
\affil[18]{National Laboratory of Genomics for Biodiversity (LANGEBIO),
    Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico}
% Saunack
\affil[19]{FIXME: SAUNACK's AFFILIATION}
% Thibaut
\affil[20]{FIXME: THIBAUT's AFFILIATION}
% Kevin
\affil[21]{Ecology and Evolutionary Biology, University of California at Irvine}
% Hugo
\affil[22]{FIXME HUGO's AFFILIATION}
% Jere
\affil[23]{FIXME: JERE'S AFFILIATION}
% Peter (second affil)
\affil[24]{Department of Mathematics, University of Oregon}

@@

\section*{Acknowledgements}
JK is supported by the Robertson Foundation.
Jere Koskela is supported in part by EPSRC grant EP/R044732/1.
ADK was supported by NIH awards R01GM117241 and R01HG010774.
Franz Baumdicker is funded by the Deutsche Forschungsgemeinschaft
EXC 2064/1 -- Project number 390727645, and EXC 2124 -- Project number 390838134.
Graham Gower was supported by a Villum Fonden Young Investigator award to Fernando Racimo (project no. 00025300).
BE was supported by  DFG grant  273887127 through Priority
Programme SPP 1819: Rapid Evolutionary Adaptation (grant STE 325/17-2); BE would also like to acknowledge  funding through The Icelandic Research
Centre (Rann{\'i}s) through an Icelandic Research Fund Grant of  Excellence nr.\ 185151-051.
